### 2017-07-26 background.tex
Adding the eScience ref to Kotta

\NAME is cloud hosted data-enclave designed to enable computation over sensitive datasets
in a cost effective and secure manner. In prior work we demonstrated the variety of ways in which \NAME offers
a scalable solution to match the compute needs of a distributed research network. \eamon{Cite everything??}
However, our extant model involved only two classes of user: 1) the administrators who take on the role of managing
data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
who are the consumers of data, performing the role of analyzing and interrogating data
via analysis pipelines.

>>>>

\NAME is cloud hosted data-enclave designed to enable computation over sensitive datasets
in a cost effective and secure manner. In prior work we demonstrated the variety of ways in which \NAME offers
a scalable solution to match the compute needs of a distributed research network ~\cite{babuji2016cloud, babuji2016secure}.
However, our extant model involved only two classes of user: 1) the administrators who take on the role of
managing data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
who are the consumers of data, performing the role of analyzing and interrogating data
via analysis pipelines.
